%-------------------------
% Resume in Latex
% Author : Laurenz Luke Gonzales
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeEdu}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{\small#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Laurenz Luke Gonzales} \\ \vspace{1pt}
    \small +1-984-255-4785 $|$ 104 Bright Sand Ct, Cary, NC 27519 \\
    \href{mailto:laurenzpg@gmail.com}{\underline{laurenzpg@gmail.com}} $|$ 
    \href{https://linkedin.com/in/laurenzlukegonzales}{\underline{Linkedin: laurenzlukegonzales}} $|$
    \href{https://github.com/lgonza32}{\underline{GitHub: lgonza32}} 
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeEdu
      {University of North Carolina - Charlotte}{Charlotte, NC}
      {Bachelor of Science (BS) in Computer Science, Software Engineering}{Graduation Date: May 2022}
      {Bachelor of Arts (BA) in Japanese Studies}{Graduation Date: May 2022}
    \small{\item{
      \textbf{GPA}{: 3.86} \\
      \textbf{Honors}{: Magna Cum Laude, Chancellor's List, Dean's List} \\
      }}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Coral Reef Restoration Capstone} $|$ \emph{Android Application}}{May 2022}
          \resumeItemListStart
            \resumeItem{Allowed the Coral Restoration Foundation to track climate change effects on coral reefs by
            working in a 5-person team environment to create a coral reef database solution.}
            \resumeItem{Designed ease of data access and entry for coral reef researchers out in the field through
            \emph{Java} with OpenWeather and Meteomatics API implementation.}
            \resumeItem{Coordinated an Agile SDLC team environment through bi-weekly sprints to help the team
            efficiently work and produce deliverables on time.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Nihon Club Websites} $|$ \emph{Webpage Application}}{December 2021}
          \resumeItemListStart
            \resumeItem{Collaborated with officers of the Nihon Club to design two websites for UNCC students and
            Japanese professors to promote Nihon Club events.}
            \resumeItem{Created simple websites with \emph{HTML}, \emph{CSS}, and \emph{JavaScript} with the goal of user experience
            and accessibility.}
            \resumeItem{Implemented a solution with \emph{Express} and \emph{MongoDB JavaScript} frameworks where Nihon Club
            officers and members can post events to promote upcoming community events.}
          \resumeItemListEnd
      \resumeProjectHeading
        {\textbf{HR Employees} $|$ \emph{Database Application}}{July 2021}
        \resumeItemListStart
          \resumeItem{Developed a database solution for a human resources coordinator 
          to keep track of employee contact information, position, salary, and performance reviews.}
          \resumeItem{Created a site map and ERD diagram to design a web application written 
          in \emph{HTML} and \emph{PHP} to clarify the functionalities of the website.}
          \resumeItem{Converted over 200 lines of employee CSV data into \emph{SQL} statements so that a 
          human resource coordinator can access and edit employee information within the company through the app.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------
\section{Leadership Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Nihon Club Officer $|$ \textmd{\emph{Secretary \& Vice-President}}}{August 2020 -- May 2022}
      {UNC Charlotte}{Charlotte, NC}
      \resumeItemListStart
        \resumeItem{Organized monthly events with 100+ attendees by managing event logistics and providing engagement 
        to Nihon Club Members about the Japanese culture.}
        \resumeItem{Coordinated with UNC Charlotte student services and the Japanese Studies department to secure 
        adequate space and promotion for Nihon Club events.}
        \resumeItem{Created an online social environment for 100+ members through the use of Discord to provide 
        online Nihon Club events during the COVID-19 pandemic.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Junior Golf Coach Volunteer}{June 2016 -- June 2018}
      {The First Tee of the Triangle}{Raleigh, NC}
      \resumeItemListStart
        \resumeItem{Participated in a professional environment as a junior coach to teach 100+ young
        first-tee participants core values, healthy habits, and valuable life skills by using golf.}
        \resumeItem{Collaborated with dozens of First Tee coaches and volunteers in First Tee
        events and weekly golf classes to create relationships with First Tee
        participants.}
        \resumeItem{Selected as the junior volunteer of the year in 2017 for the shown impact and dedication
        to the First Tee of the Triangle chapter and participants around the Triangle.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, Python, SQL (MySQL), HTML/CSS, PHP, JSON, EJS} \\
     \textbf{Frameworks}{: Node.js, Express, MongoDB, JUnit} \\
     \textbf{Developer Tools}{: VS Code, Eclipse, Git/GitHub} \\
     \textbf{Libraries}{: JQuery, Mongoose} \\
     \textbf{Certification}{: TestOut Security Pro \hfill{June 2020}} \\
    }}
 \end{itemize}


%-----------Skills/INTERESTS-----------
\section{Skills/Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Skills}{: Japanese Language \& Business, Microsoft Office (Word, Excel, PowerPoint), Agile Project Management} \\
   \textbf{Interests}{: Golf, Japanese Studies, Globalization, Community Building} \\
  }}
\end{itemize}

%-------------------------------------------
\end{document}